Containers and R---the Rockerverse and beyond

### 2019-11-28 manuscript.Rmd
some cleanup

These issues can be mitigated by deploying not a single container, but a _cluster_ of containers, orchestrated as a single deployment. The deployment system of choice at the time of writing is [Kubernetes](https://kubernetes.io). This allows you to deploy a single image to a pool of servers, which can then serve requests in parallel. Client-side requests are made to the cluster ingress endpoint, which then redircts them to individual servers. The orchestrator can identify nodes that have failed, and restart them automatically; it can also detect when there is no capacity to service more requests, and start additional containers as needed.

@@

An example of an R package for working with containers in the cloud is AzureContainers, which interacts with three Azure services: Container Instances (for running a single container), Container Registry (a private docker registry service), and Kubernetes Service (for Kubernetes on Azure). AzureContainers provides a powerful interface that builds on the framework provided by AzureRMR, which is an overarching package for working with Resource Manager, the framwork for deploying and managing arbitrary resource in Azure. On the client side, it provides simple shells to the Docker, Kubectl and Helm tools that are commonly used for managing containers and Kubernetes clusters.

>>>>

These issues can be mitigated by deploying not a single container, but a _cluster_ of containers, orchestrated as a single deployment. The deployment system of choice at the time of writing is [Kubernetes](https://kubernetes.io). This allows you to deploy a single image to a pool of servers, which can then serve requests in parallel. Client-side requests are made to the cluster ingress endpoint, which then redirects them to individual servers. The orchestrator can identify cluster nodes that have failed, and restart them automatically; it can also detect when there is no capacity to service more requests, and start additional servers and containers as needed.

@@

An example of an R package for working with containers in the cloud is AzureContainers, which interacts with three Azure services: Container Instances (for running a single container), Container Registry (a private docker registry service), and Kubernetes Service (for Kubernetes on Azure). AzureContainers provides a lightweight yet powerful interface for working with Resource Manager, the framework for deploying and managing arbitrary resources in Azure. On the client side, it provides simple shells to the Docker, Kubectl and Helm tools that are commonly used for managing containers and Kubernetes clusters.
